%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DONT BREAK THIS FILE INTO PIECES LIKE THE REST OF THE SECTIONS %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% This template illustrates organizing the functional requirements for the 
% product by system features, the major services provided by the product. 
% You may prefer to organize this section by use case, mode of operation, 
% user class, object class, functional hierarchy, or combinations of these, 
% whatever makes the most logical sense for your product.

\chapter{Functional Requirements} \label{chap:systemfeatures}


\section{Configuration Manager}
TODO: Description of configuration manager. \todo{Add description for configuration manager}

\requirementreset % reset the requirement counter
\requirement{CONFIG}{
	A default configuration will be generated and saved to disk if one is not 
	found on the system.
}

\requirement{CONFIG}{
	Invalid or malformed configuration files will not crash the game engine.
}

\requirement{CONFIG}{
	Invalid or malformed configuration files will be reported and cause the 
	engine to exit gracefully.
}

\requirement{CONFIG}{
	Configuration options stored in the configuration file will be exposed via 
	a settings GUI available for display and modification.
}

\requirement{CONFIG}{
	Modifying the configuration options will through the GUI will immediately 
	update the configuration file.
}

\unsure{Are there any more requirements needed for config manager?}







\newpage
\section{Asset Managemer}
Description TODO

\requirementreset % reset the requirement counter
\requirement{ASSETS}{
	The assets manager will load assets defined 
}



\subsection{MPQ Archive Manager}
\paragraph{MPQ-1}
\begin{indentpar}{1cm}
Must be able to extract all files from the archive, regardless of the file type.
\end{indentpar}



\subsection{File Cache}

\newpage
\subsection{}

\newpage
\section{Audio Engine}

\newpage
\section{GUI Toolkit}

\newpage
\section{Input Backend}

\newpage
\section{Map Engine}

\newpage
\section{Rendering Backend}

\newpage
\section{Screen Manager}

\newpage
\section{Terminal \& Shell}

\newpage
\section{Scripting Language Interpretter}

\newpage
\section{Network Game Client}

\newpage
\section{Network Game Server}

\newpage
\section{Network Protocol}

